|

### 2021-03-14 appendix/appendix.Rmd
add funnel plot and egger et al tests first model

[^freire]: Independent Researcher, <danilofreire@gmail.com>, <https://danilofreire.github.io>. Corresponding author.

@@

# Install if not already installed
install <- function(x) {
  if (x %in% rownames(installed.packages()) == FALSE)
    install.packages(x, dependencies = T,
                     repos = "http://cran.us.r-project.org")
}
lapply(pkgs, install)
devtools::install_github("isubirana/compareGroups")

# Load packages
lapply(pkgs, require, character.only = T)
library("compareGroups")

@@

@@

```{r, size="footnotesize", warning=F, message=F, echo = FALSE, cache=TRUE}
fulldat$usemeta2 <- factor(fulldat$usemeta)
levels(fulldat$usemeta2) <- c("Other Coefficients", "Main Coefficients")
aux <- select(fulldat, usemeta2, indepvar2, year, published,
              elecsys2, method) %>%
  rename(`Independent Variables` = indepvar2,
         `Year` = year,
         `Published work` = published,
         `Electoral system` = elecsys2,
         `Estimation method` = method)

descrTable(~.-usemeta2, aux, y = aux$usemeta2,
           show.p.overall = F, show.all = T)
```

@@

In all empirical estimates, we use the package `meta`, and the package `dmetar`, described in [Doing Meta-Analysis with R](https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/random.html). To empirically implement the random effects model, we need to choose a method to estimate the true effect size variance, $\tau^2$, which in our formulation, represents the variance of $\xi_i$. We selected the **Restricted Maximum Likelihood Estimator**, as the literature regards it the most precise when analysing continuous measures, such as we have in our data.

@@

@@

>>>>

[^freire]: Independent Researcher, <danilofreire@gmail.com>, <https://danilofreire.github.io>.

@@

# Install if not already installed
install <- function(x) {
  if (x %in% rownames(installed.packages()) == FALSE)
    install.packages(x, dependencies = T,
                     repos = "http://cran.us.r-project.org")
}
lapply(pkgs, install)
devtools::install_github("isubirana/compareGroups")
devtools::install_github("MathiasHarrer/dmetar")

# Load packages
lapply(pkgs, require, character.only = T)
library("compareGroups"); library(dmetar)

@@

\newpage

@@

```{r, warning=F, message=F, echo = FALSE, cache=TRUE}
fulldat$usemeta2 <- factor(fulldat$usemeta)
levels(fulldat$usemeta2) <- c("Other Coefficients", "Main Coefficients")
aux <- select(fulldat, usemeta2, indepvar2, year, published,
              elecsys2, method) %>%
  rename(`Independent Variables` = indepvar2,
         `Year` = year,
         `Published work` = published,
         `Electoral system` = elecsys2,
         `Estimation method` = method)

export2md(descrTable(~.-usemeta2, aux, y = aux$usemeta2,
                        show.p.overall = F, show.all = T), caption = "Descriptive Statistics of Moderators")
```

@@

In all empirical estimates, we use the package `meta`, and the package `dmetar`, described in [Doing Meta-Analysis with R](https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/random.html). To empirically implement the random effects model, we need to choose a method to estimate the true effect size variance, $\tau^2$, which in our formulation, represents the variance of $\xi_i$. We selected the **Restricted Maximum Likelihood Estimator**, as the literature regards it the most precise when analysing continuous measures, such as we have in our data (XXXX TO UMBERTO: PUT CITATION HERE).

@@

And to assess the possibility of publication bias, we add funnel plot below:

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod, contour = c(.95,.975,.99),
       col.contour=c("darkblue","blue","lightblue"))
legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
       fill=c("darkblue","blue","lightblue"))
```

@@

1.  The results are highly heterogeneous: $I^2 =$ `r round(mod$I2*100, 2)`.
2.  The estimated SMD in the random effects model is $g =$ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
3.  The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
4. The @egger1997bias test `r ifelse(eggers.test(mod)$p<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.
